Methods paper for erosion

### 2017-12-07 docs/methods/erosion_methods.tex
NM

In order to regularize boundary evolution, we modify the normal velocity
in Eq.~\eqref{eqn:bodyEvolution} as follows
\begin{equation}
\label{eqn:Vn}
\Vn = \atau + \eps \mean{\atau} \left( \frac{L \kappa}{2\pi} - 1 \right)
%\Vn = \atau + \frac{\eps}{\log \left(2\pi/L \right)} \left(\kappa - \frac{2 \pi}{L} \right)
\end{equation}
Here, $\kappa$ is the curvature, $\eps$ is a small parameter, and $L$ is the total arc length of the body, and $\mean{\cdot}$ indicates a surface mean. The second term on the right acts to smooth bodies with high-frequency oscillations by introducing a {\em curvature}-dependent component in the interface velocity. Since a closed body has a mean curvature of $\mean{\kappa} = 2\pi / L$, the term in parentheses has mean zero. Thus, this term is area-preserving, so that the only material loss is due to the shear stress itself. In addition, we have scaled this term on the $\mean{\atau}$, the average absolute stress, so that it is always proportional to the true source of erosion $\atau$, even as bodies vanish (reword).

@@

Next, at the second stage of RK2, we discretize as
\begin{align}
& \frac{L^{(n+1)} - L^{(n)}}{\Dt} = \Mterm^{(n+1/2)} \\
& \frac{ \mu_k^{(n+1)} \thhat_k^{(n+1)} - \thhat_k^{(n)}}{\Dt} = \mu_k^{(n+1/2)} \hat{\NLterm}_k^{(n+1/2)}
\end{align}
We again compute the integrating factor, $\mu_k^{(n+1)}$ via the ( insert integration rule), giving
\begin{align}
\thhat_k^{(n+1)} = 
& \thhat_k^{(n)}
\exp \left( - \epsilon k^2 \Dt \elfun^{(n+1/2)} \right) +  \\
& \Dt \, \hat{\NLterm}_k^{(n+1/2)}
\exp \left( - \frac{1}{4} \eps k^2 \Dt \left( 3 \elfun^{(n+1/2)} - \elfun^{(n)} \right) \right)
\end{align}

\newpage
\todo[inline]{Artificial Diffusion} 
\todo[inline]{Gaussian Filter}

@@

>>>>

In order to regularize boundary evolution, we modify the normal velocity
in Eq.~\eqref{eqn:bodyEvolution} as follows
\begin{equation}
\label{eqn:Vn}
\Vn = \atau + \eps \mean{\atau} \left( \frac{L }{2\pi} \kappa - 1 \right)
\end{equation}
Here, $\kappa$ is the curvature, $\eps$ is a small parameter, and $L$ is the total arc length of the body, and $\mean{\cdot}$ indicates a surface mean. The second term on the right acts to smooth bodies with high-frequency oscillations by introducing a {\em curvature}-dependent component in the interface velocity. Since a closed body has a mean curvature of $\mean{\kappa} = 2\pi / L$, the term in parentheses has mean zero. Thus, this term is area-preserving, so that the only material loss is due to the shear stress itself. In addition, we have scaled this term on the $\mean{\atau}$, the average absolute stress, so that it is always proportional to the true source of erosion $\atau$, even as bodies vanish (reword).

@@

Next, at the second stage of RK2, we discretize as
\begin{align}
& \frac{L^{(n+1)} - L^{(n)}}{\Dt} = \Mterm^{(n+1/2)} \\
& \frac{ \mu_k^{(n+1)} \thhat_k^{(n+1)} - \thhat_k^{(n)}}{\Dt} = \mu_k^{(n+1/2)} \hat{\NLterm}_k^{(n+1/2)}
\end{align}
We again compute the integrating factor, $\mu_k^{(n+1)}$ via the ( insert integration rule), giving
\begin{align}
\thhat_k^{(n+1)} = 
& \thhat_k^{(n)}
\exp \left( - \epsilon k^2 \Dt \elfun^{(n+1/2)} \right) +  \\
& \Dt \, \hat{\NLterm}_k^{(n+1/2)}
\exp \left( - \frac{1}{4} \eps k^2 \Dt \left( 3 \elfun^{(n+1/2)} - \elfun^{(n)} \right) \right)
\end{align}
\todo[inline]{Gaussian Filter}

@@

\subsection{Single-body validation results}

\subsubsection{The uniform stress geometry}

\subsubsection{The vanishing rate of area}
In three-dimensional Stokes flow, the shear stress vanishes as
\begin{equation}
\tau_{3D} \sim \mu V/L
\end{equation}
However, this law must be modified for 2D flow, which represents 3D bodies of large extent. As the body vanishes, the walls have an ever decreasing influence. Thus, the stress must be consistent with free-space slender-body theory as it vanishes. The stress law consistent with slender body theory (a long cylinder held perpendicular to a flow) is
\begin{equation}
\tau_{2D} \sim \frac{4 \pi \mu V}{L \log(W/L)}
\end{equation}

% NEWPAGE
\newpage
